$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-09-16 paper/paper.tex
Add Orchard's encoding of effects into session types
Swap green for darkgray

\begin{figure}[t]
  \small
  \centering
  \begin{tikzpicture}[draw,circle]
    \node[draw,circle,fill opacity=0.3,text opacity=1,fill=orange] (send-x) at (0,2)   {$\func{send} \, x$};
    \node[draw,circle,fill opacity=0.3,text opacity=1,fill=orange] (send-y) at (2,2)   {$\func{send} \, y$};
    \node[draw,circle,fill opacity=0.3,text opacity=1,fill=green] (recv-z) at (4,2)   {$\func{recv} \, z$};
    \node[draw,circle,fill opacity=0.3,text opacity=1,fill=blue,align=center] (sync) at (2,0)   {$\func{carry}$\\$ \, x \, y \, z$};

    \draw[->] (send-x) -- node[left] {$x$} (sync);
    \draw[->] (send-y) -- node[right] {$y$} (sync);
    \draw[->] (sync.35) -- node[right] {$z$} (recv-z.240);
    \draw[->] (sync) -- (recv-z);
  \end{tikzpicture}
  \caption{The courier system: two \textcolor{orange}{senders} $S_1$ and $S_2$, one \textcolor{green}{receiver} $R$ and one \textcolor{blue}{courier} $C$.}
  \label{fig:example-process}
\end{figure}

@@

>>>>

\begin{figure}[t]
  \small
  \centering
  \begin{tikzpicture}[draw,circle]
    \node[draw,circle,fill opacity=0.3,text opacity=1,fill=orange] (send-x) at (0,2)   {$\func{send} \, x$};
    \node[draw,circle,fill opacity=0.3,text opacity=1,fill=orange] (send-y) at (2,2)   {$\func{send} \, y$};
    \node[draw,circle,fill opacity=0.3,text opacity=1,fill=darkgray] (recv-z) at (4,2)   {$\func{recv} \, z$};
    \node[draw,circle,fill opacity=0.3,text opacity=1,fill=blue,align=center] (sync) at (2,0)   {$\func{carry}$\\$ \, x \, y \, z$};

    \draw[->] (send-x) -- node[left] {$x$} (sync);
    \draw[->] (send-y) -- node[right] {$y$} (sync);
    \draw[->] (sync.35) -- node[right] {$z$} (recv-z.240);
    \draw[->] (sync) -- (recv-z);
  \end{tikzpicture}
  \caption{The courier system: two \textcolor{orange}{senders} $S_1$ and $S_2$, one \textcolor{darkgray}{receiver} $R$ and one \textcolor{blue}{courier} $C$.}
  \label{fig:example-process}
\end{figure}

@@

Orchard and Yoshida \cite{OrchardY16} embed a small effectul imperative language into the session-typed \picalc{}, showing that session types are expressive enough to encode effect systems.
